Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-01-23 AO_bondedSi.tex
more DTJ edits including a typo in Title of Figure 1

\subsection{What level do you need to measure to}
For all types of gaps and bubbles, our technique needs to provide an accurate assessment of the transmission loss at the operating wavelength.  For finite-sized bubbles, measurement of the axial dimension helps us to assess the effects of high-temperature annealing on removal of hydrogen bubbles.  A wavelength-dependent transmission variation can also indicate the presence of large numbers of gaps that are too small to resolve spatially, as one might expect if there are many very small contaminants present along the interface.  An important figure of merit for a bond is whether any loss due to gaps is smaller than the loss one might expect from two passages through a reasonably effective broad-band anti-relfection coating in the infrared.  To meet this diagnostic goal, our technique must be able to characterize gaps with losses of a few percent at the operating wavelength.  A 2\% loss at 1.15 $\mu$m corresponds to a gap of XX nm at normal incidence and the gap size for a loss of this magnitude scales linearly with wavelength.  We therefore need to be able to measure transmission as a function of wavelength to a fraction of a percent, including all systematic errors, for devices operating near 1 $\mu$m and to a somewhat looser standard for devices operating at longer wavelengths.

@@

Our measurement technique exploits the large Fresnel reflection \cite{2001opt4.book.....H} at the Si$-$vacuum interface.  The refractive index of silicon at room temperature ranges from 3.55$-$3.45 from $\lambda = $ 1150$-$2500 nm \cite{2006SPIE.6273E..77F}, one of the largest refractive indices of any conventional material.  The Fresnel reflection is about 30\% per surface.  For comparison, conventional optical materials with refractive indices in the range 1.5$-$1.7 have Fresnel reflection of merely 4$-$7\% per surface.  Figure \ref{figSiIndexFinesse} shows the refractive index as a function of wavelength for room temperature, which we computed using the coefficients from \cite{2006SPIE.6273E..77F}.

>>>>

\subsection{What level do you need to measure to}
For all types of gaps and bubbles, our technique needs to provide an accurate assessment of the transmission loss at the operating wavelength.  For finite-sized bubbles, measurement of the axial dimension helps us to assess the effects of high-temperature annealing \cite{Horn2009, Masteika2014} on removal of hydrogen bubbles.  A wavelength-dependent transmission variation can also indicate the presence of large numbers of gaps that are too small to resolve spatially, as one might expect if there are many very small contaminants present along the interface.  Our technique must be able to characterize gaps with losses of a few percent at the operating wavelength.  A 2\% loss at 1.15 $\mu$m corresponds to a gap of XX nm at normal incidence and the gap size for a loss of this magnitude scales linearly with wavelength.  We therefore need to be able to measure transmission as a function of wavelength to a fraction of a percent, including all systematic errors, for devices operating near 1 $\mu$m and to a somewhat looser standard for devices operating at longer wavelengths.

@@

Our measurement technique exploits the large Fresnel reflection \cite{2001opt4.book.....H} at the Si$-$vacuum interface.  The refractive index of silicon at room temperature ranges from 3.55$-$3.45 from $\lambda = $ 1150$-$2500 nm \cite{2006SPIE.6273E..77F}, one of the largest refractive indices of any conventional material.  The Fresnel reflection is about 30\% per surface, much larger than the $4-7\%$ per surface of the many optical materials with refractive indices in the range $1.5-1.7$.  Figure \ref{figSiIndexFinesse} shows the refractive index as a function of wavelength for room temperature,  computed using the coefficients from \cite{2006SPIE.6273E..77F}.
